---
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Welcome to our survey!

We would like to know a little bit about you so that we only ask questions relevant to your expertise.  

```{r respondent DOI region}
sd_question(
  type   = 'mc_buttons',
  id     = 'respondent_FC_region',
  direction = 'vertical', 
  label  = "Which region is your fanclub primarily located in?",
  option = c(
    "11 Alaska" = 11
  )
)
```

```{r}
sd_next(label = 'Head to my regions survey')
```

:::

::: {#Alaska_lennon_birth .sd-page}

### Region 11 - Alaska - Lennon birth year

What year was john lennon born in? 

```{r}
sd_question(type  = "numeric", id = 1, label = "john lennons birth year?")
```

```{r}
sd_next(next_page = 'Alaska_mccartney_birth')
```
:::

::: {#Alaska_mccartney_birth .sd-page} 

### Region 11 - Alaska - mccartney birth year

What year was paul mccartney born in? 

```{r}
sd_question(type  = "numeric", id = 2,  label = "paul mccartneys birth year?")
```

```{r}
sd_next(next_page = 'Alaska_ringosdingos')
```
::: 

::: {#Alaska_ringosdingos .sd-page} 

### Region 11 - Alaska - ringosdingos 

How many dingos did ringo starr own? 

```{r}
sd_question(type  = "numeric", id = 3, label = "How many dingos")
```

```{r}
sd_next(next_page = 'end')
```

::: 

::: {#end .sd-page}
## End

This it the last page in the survey. Thanks for your help, we know the data are a little nebulous, but it is difficult to balance responses with survey length. 

```{r}
sd_close("Exit Survey")
```

::: 
